\Title

### 2016-02-24 manuscript/manuscript.tex
More text about the differences and residuals in CRUST1

Fig.~\ref{fig:crust1-results}c shows the final solution after both
cross-validation procedures.
The recovered model is smooth, indicating that the cross-validation procedure
was effective in estimating an optimal regularization parameter.
Fig.~\ref{fig:crust1-results}d shows the difference between
the true Moho depth shown in Fig.~\ref{fig:crust1-data}a
and the estimate.
The maximum and minimum differences are, respectively,
9.8 and -8.2 km.

>>>>

Fig.~\ref{fig:crust1-results}c shows the final solution after both
cross-validation procedures.
The recovered model is smooth, indicating that the cross-validation procedure
was effective in estimating an optimal regularization parameter.
Fig.~\ref{fig:crust1-results}d shows the difference between
the true Moho depth shown in Fig.~\ref{fig:crust1-data}a
and the estimate.
The maximum and minimum differences are, respectively,
9.8 and -8.2 km.
The largest absolute differences are located along the central and northern
Andes, where there is a sharp increase in the true Moho depth.
Positive differences (indicating a too shallow estimate)
appear along the central portion of the Andes,
flanked by regions of negative differences (indicating a too deep estimate)
on the continental and Pacific sides.
Figs.~\ref{fig:crust1-results}e and g show the inversion residuals (difference
between the observed and predicted data).
The inversion residuals appear normally distributed,
with 0.03 mGal mean and a standard deviation of 4.10 mGal.
The residuals follow the same pattern as the differences shown in
Fig.~\ref{fig:crust1-results}d,
with the largest residuals (in absolute value) along the Andes.
The pattern of the residuals is inverted, though,
with the central portion being dominated by negative residuals
and flanked by positive residuals on both sides.
